---
title: "Jiayi Yang STAT 6210 - Final Project"
output:
  pdf_document: default
  html_notebook: default
---
Load data
```{r}
rm(list=ls())
setwd("~/Data Analysis/Project")
options(max.print=1000000)
anime = read.csv(file = "anime.csv", header = TRUE)
head(anime)
```
Have a look at data
```{r}
dim(anime)
```
```{r}
str(anime)
```
```{r}
summary(anime)
```

Load packages will be used
```{r}
library(dplyr)
library(magrittr)
library(ggplot2)
library(reshape)
library(kernlab)
```
Data cleaning 
split genre into dummy variables
```{r}
#install.packages('splitstackshape')
library(splitstackshape)
anime_split = cSplit_e(anime, "genre", ",", type = "character", fill = 0)
```
Look at the splited data
```{r}
str(anime_split)
```
```{r}
colSums(is.na(anime_split))
```

anime_split has 12,294 rows and 50 variables. I will not include the original genre and id.
Drop name, genre and id to create new dataframe, and move rating to be the last column
```{r}
drops <- c('name','anime_id','genre','rating')
anime_new = anime_split[ , !(names(anime_split) %in% drops)]
anime_new = cbind(anime_new,rating = anime_split$rating)
anime_new = tbl_df(anime_new)
str(anime_new)
```


change factor to number,drop na and build matrix(only rating has na, since I will use rating as my dependent variable in my regression model, I decide to not use rows contain na in rating)
```{r}
aniMat = na.omit(anime_new)
aniMat$episodes = as.numeric(aniMat$episodes)
aniMat$type = as.numeric(aniMat$type)
str(aniMat)
```
see dist of each variable
```{r}
set.seed(1234)
aniMat = as.data.frame(aniMat)
aniMat.melt <- melt(aniMat)
ggplot(aniMat.melt,aes(x=value))+geom_density()+facet_wrap(~variable,scales="free")
ggplot(aniMat.melt,aes(x=value))+geom_histogram()+facet_wrap(~variable,scales="free")
```
confidence interval of rating
```{r}
#cannot use shapiro test to test normality because sample size is larger than 5000
plot(density(aniMat$rating))
```
```{r}
#CI for normal approximation
t.test(aniMat$rating)
```
```{r}
#CI for bootstrap
x = aniMat$rating
xmean = mean(x)
boots = matrix(0,10000,1)
for(i in 1:10000){
  xsample = sample(x,size = 20,replace = TRUE)
  boots[i] = mean(xsample)
}
hist(boots-xmean,100)
```
```{r}
xmean+quantile(boots-xmean,c(0.05,0.95))
```

see correlation
```{r}
cor(aniMat)
```
```{r}
library(corrplot)
corrplot(cor(aniMat))
```
there are high correlations between genre_Mecha and genre_Sci-Fi, also genre_space and genre_SciFi.

plot bivariate graphs including Y
```{r}
aniMat.melt2 <- cbind(aniMat.melt,y=aniMat$rating)
ggplot(aniMat.melt2,aes(x=value,y=y))+stat_bin2d()+facet_wrap(~variable,scales="free")
```


We will now build linear models using best subset selection, forward and backward stepwise selection. After studying the residuals, we will check if any transformations are necessary.

```{r}
library(leaps)
regfit.full <- regsubsets(rating~.,aniMat,nvmax=46)
summary(regfit.full)
```

```{r}
regfit.summary <- summary(regfit.full)
names(regfit.summary)
```
```{r}
plot(regfit.summary$rsq)
```
```{r}
plot(regfit.summary$bic)
which.min(regfit.summary$bic)
```
The lowest BIC is achieved by the 28th model.
```{r}
coef(regfit.full,28)
```


We will also check the models chosen by best subset selection using cross validation.
```{r}
library(boot)
CVmse <- rep(0,46)
for(i in 1:46){
tempCols <- which(regfit.summary$which[i,-1]==TRUE)
tempCols <- c(tempCols,47)
tempCols <- as.numeric(tempCols)
tempGLM <- glm(rating~.,data=aniMat[,tempCols])
tempCV <- cv.glm(tempGLM,data=aniMat[,tempCols],K = 10)
CVmse[i] <- tempCV$delta[1]
}
plot(CVmse)
print(which.min(CVmse))
print(min(CVmse))
print(CVmse)
```

Forward Stepwise Selection
```{r}
regfit.fwd <- regsubsets(rating~.,aniMat,nvmax=46,method="forward")
summary(regfit.fwd)
```

```{r}
regfit.fwd.summary <- summary(regfit.fwd)
which.min(regfit.fwd.summary$bic)
```

Backward Stepwise Selection
```{r}
regfit.bwd <- regsubsets(rating~.,aniMat,nvmax=46,method="backward")
summary(regfit.bwd)
```
```{r}
regfit.bwd.summary <- summary(regfit.bwd)
which.min(regfit.bwd.summary$bic)
```
LASSO
```{r}
library(glmnet)
lasso.cv <- cv.glmnet(x=as.matrix(aniMat[,-47]),y=as.matrix(aniMat[,47]),alpha=1,nfolds = 10)
plot(lasso.cv)
print(min(lasso.cv$cvm))
```
The lost mse from LASSO is a little bit higher than the one I obtained with best subset selection.So the best model up to now is from best subset selection.

Ridge Regression
```{r}
library(glmnet)
ridge.cv <- cv.glmnet(x=as.matrix(aniMat[,-47]),y=as.matrix(aniMat[,47]),alpha=0,nfolds = 10)
rid.fit = cv.glmnet(x=as.matrix(aniMat[,-47]),y=as.matrix(aniMat[,47]),family="gaussian", alpha=0)
min(rid.fit$cvm)
```


```{r}
setnames(aniMat, "genre_Slice of Life", "genre_SliceofLife")
setnames(aniMat, "genre_Sci-Fi", "genre_SciFi")
```
Nonlinear effects
check if any nonlinear transformations are necessary. first start by fitting the linear model.Since the feature selection gives me two models: 28th and 34th. I will build both two models to compare the results.
```{r}
#model for 34th
lm1 <- lm(rating ~. -genre_Vampire-genre_Yaoi-genre_Yuri-genre_Space-`genre_Shoujo Ai`-genre_Samurai-`genre_Martial Arts`-genre_Mecha-genre_Harem-genre_Demons-genre_Game-genre_Cars, data=aniMat)
```

```{r}
aniMat.melt3 <- cbind(aniMat.melt,resid=lm1$residuals)
ggplot(aniMat.melt3,aes(x=value,y=resid))+geom_point()+geom_smooth(method="loess")+facet_wrap(~variable)
```
There are obvious non-linearities with respect to members.
```{r}
#model for 28th
lm2 <- lm(rating ~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+members+genre_Action+genre_Adventure+genre_Comedy, data=aniMat)
aniMat.melt4 <- cbind(aniMat.melt,resid=lm2$residuals)
ggplot(aniMat.melt4,aes(x=value,y=resid))+geom_point()+geom_smooth(method="loess")+facet_wrap(~variable)
```
There are obvious non-linearities with respect to members.



```{r}
#chose number of ploy for lm1
memMSE <- rep(0,5)
for(i in 1:5){
templm <- glm(rating ~. -genre_Vampire-genre_Yaoi-genre_Yuri-genre_Space-`genre_Shoujo Ai`-genre_Samurai-`genre_Martial Arts`-genre_Mecha-genre_Harem-genre_Demons-genre_Game-genre_Cars-members+poly(members,i), data=aniMat)
tempCV <- cv.glm(aniMat,templm,K = 10)
memMSE[i] <- tempCV$delta[1]
}
plot(memMSE)
print(which.min(memMSE))
print(min(memMSE))
```
Minimum is obtained with a 4th degree polynomial for members with MSE equal 0.6333695. So include it.
```{r}
#chose number of ploy for lm2
memMSE <- rep(0,5)
for(i in 1:5){
templm <- glm(rating ~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+poly(members,i), data=aniMat)
tempCV <- cv.glm(aniMat,templm,K = 10)
memMSE[i] <- tempCV$delta[1]
}
plot(memMSE)
print(which.min(memMSE))
print(min(memMSE))
```
Minimum is obtained with a 4th degree polynomial for members with MSE equal 0.6354152.So include it and compare them.

Final model with members 4th
```{r}
finalLm <- lm(rating ~. -genre_Vampire-genre_Yaoi-genre_Yuri-genre_Space-`genre_Shoujo Ai`-genre_Samurai-`genre_Martial Arts`-genre_Mecha-genre_Harem-genre_Demons-genre_Game-genre_Cars-members+poly(members,4), data=aniMat)
summary(finalLm)
```
```{r}
finalLm2 <- lm(rating~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+poly(members,4), data=aniMat)
summary(finalLm2)
anova(finalLm,finalLm2,test="F")
```
anova test shows my second model is better.

```{r}
finalGLM<- glm(rating ~. -genre_Vampire-genre_Yaoi-genre_Yuri-genre_Space-`genre_Shoujo Ai`-genre_Samurai-`genre_Martial Arts`-genre_Mecha-genre_Harem-genre_Demons-genre_Game-genre_Cars-members+poly(members,4), data=aniMat)

finalGLM2<- glm(rating~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+poly(members,4), data=aniMat)
```

```{r}
cv.glm(aniMat,finalGLM,K=10)$delta[1]
cv.glm(aniMat,finalGLM2,K=10)$delta[1]
```
MSE also shows my second model is better. Also my MSE decreases from 0.69 to 0.63.

```{r}
library(car)
qqPlot(finalLm2)
```

```{r}
plot(finalLm2,which=4)
```



```{r}
aniMat[c(41,87,805),]
```

We try removing these outliers and fitting the model again.
```{r}
finalLmWO <- lm(rating~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+poly(members,4), data=aniMat[-c(41,87,805),])
summary(finalLmWO)
```


```{r}
qqPlot(finalLmWO)
```


check for homoskedasticity
```{r}
library(car)
ncvTest(finalLm2)
```
```{r}
ncvTest(finalLmWO)
```

```{r}
boot.fn <- function(data,index){
tempLm <- lm(rating~genre_Supernatural+genre_SliceofLife+genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+poly(members,4),data=data,subset=index)
tempCoef <- coef(tempLm)
return(tempCoef)
}
boot(aniMat,boot.fn,R=1000)
```
Splines
```{r}
library(mgcv)
library(gamclass)
library(ggplot2)
```


```{r}
aniMat = as.data.frame(aniMat)
gam.a<- gam(rating~genre_Supernatural+genre_SliceofLife +genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+episodes+genre_Action+genre_Adventure+genre_Comedy+s(members), data = aniMat)
summary(gam.a)
```

```{r}
CVgam(formula(gam.a),aniMat,nfold=10)
anova(finalLm2,gam.a,test="F")
```
MSE becomes 0.5822 now.
Try add spline on episodes.
```{r}
gam.a2<- gam(rating~genre_Supernatural+genre_SliceofLife +genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+s(episodes)+genre_Action+genre_Adventure+genre_Comedy+s(members), data = aniMat)
summary(gam.a2)
CVgam(formula(gam.a2),aniMat,nfold=10)
anova(gam.a,gam.a2,test="F")
```
MSE becomes 0.5761 now.
```{r}
plot(gam.a2)
```

```{r}
memList <- list()
memList[[1]] <- gam(rating ~ genre_Supernatural + genre_SliceofLife + genre_Sports + 
    genre_Shoujo + genre_Shounen + genre_Romance + genre_School + 
    genre_SciFi + genre_Seinen + genre_Music + genre_Mystery + 
    genre_Police + genre_Psychological + genre_Kids + genre_Military + 
    genre_Hentai + genre_Historical + genre_Horror + genre_Josei + 
    genre_Dementia + genre_Drama + genre_Fantasy + type + s(episodes) + 
    genre_Action + genre_Adventure + genre_Comedy + members,data=aniMat)
for(i in 2:10){
memList[[i]] <- gam(rating ~ genre_Supernatural + genre_SliceofLife + genre_Sports + 
    genre_Shoujo + genre_Shounen + genre_Romance + genre_School + 
    genre_SciFi + genre_Seinen + genre_Music + genre_Mystery + 
    genre_Police + genre_Psychological + genre_Kids + genre_Military + 
    genre_Hentai + genre_Historical + genre_Horror + genre_Josei + 
    genre_Dementia + genre_Drama + genre_Fantasy + type + s(episodes) + 
    genre_Action + genre_Adventure + genre_Comedy + s(members,k=i+1),data=aniMat)
}
memMSE <- rep(0,10)
for(i in 1:10){
memMSE[i] <- CVgam(formula(memList[[i]]),aniMat)$cvscale
}
```
k=10 gives lowest mse 
```{r}
gam.a2.final<- gam(rating~genre_Supernatural+genre_SliceofLife +genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+type+s(episodes)+genre_Action+genre_Adventure+genre_Comedy+s(members,k=10), data = aniMat)
summary(gam.a2.final)
CVgam(formula(gam.a2.final),aniMat,nfold=10)
plot(gam.a2.final)
```

Interaction terms
Remember that type and episodes had 45% correlation.
```{r}
ggplot(aniMat,aes(x=type,y=episodes))+stat_density2d()
```


```{r}
gam.a2.final2<- gam(rating~genre_Supernatural+genre_SliceofLife +genre_Sports+genre_Shoujo+
genre_Shounen+genre_Romance+genre_School+genre_SciFi+genre_Seinen+genre_Music+genre_Mystery+
genre_Police+genre_Psychological+genre_Kids+genre_Military+genre_Hentai+genre_Historical+genre_Horror+genre_Josei+
genre_Dementia+genre_Drama+genre_Fantasy+s(episodes,type)+genre_Action+genre_Adventure+genre_Comedy+s(members,k=10), data = aniMat)
summary(gam.a2.final2)
CVgam(formula(gam.a2.final2),aniMat,nfold=10)
```
Lower MSE 0.5709
```{r}
plot(gam.a2.final2)
```
Extra method: Elastic Net with glnet 0<alpha<1

```{r}
en.fit = cv.glmnet(as.matrix(aniMat[,-47]),as.matrix(aniMat[,47]),family="gaussian", alpha=0.5)
min(en.fit$cvm)
```
Extra method:Least Angle Regression(LAR)
```{r}
#install.packages('lars')
library(lars)
mselars = cv.lars(as.matrix(aniMat[,-47]),as.matrix(aniMat[,47]),K = 10,trace = FALSE, plot.it = TRUE, se = TRUE,type = c("lar"))
min(mselars$cv)
which.min(mselars$cv)
```
The lost mse from LAR(0.6928072) is a little bit higher than the one I obtained with best subset selection.
Huge
```{r}
#install.packages('huge')
library(huge)
```
```{r}
aniMx = as.matrix(aniMat)
huge(aniMx)
h0 = huge(aniMx)
```
```{r}
plot.huge(h0)
```
```{r}
h1 = huge(aniMx,lambda = 0.1)
plot.huge(h1)
```
```{r}
h2 = huge(aniMx,lambda = 0.3)
plot.huge(h2)
```




